% Abstract for the TUM report document
% Included by MAIN.TEX


\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}	





\vspace*{2cm}
\begin{center}
{\Large \bf Abstract}
\end{center}
\vspace{1cm}

The monitoring of fish for stock assessment in aquaculture, commercial fisheries 
and in the assessment of the effectiveness of biodiversity management strategies 
such as marine protected Areas and closed area management has been thriving since the 1980s.
as does area continuously grows, it becomes important to develop a remote monitoring 
system to estimate the biomass of the large number of fishes bred in cages,
since around 80\% of all sales of farmed fish are arranged pre-harves,
that mean, the profit on the sale directly depends on correct estimations of weight,
size distribution and total biomass.
Therefore automated and relatively affordable tools for biomass estimation have to be developed.

Here, we will rely on complex stereo camera system,
compose of time of flight range camera and CCD grayscale camera,
that film fishes in the cage for certain period of time.
in order to estimate the biomass, the volume of the fish has to be estimated. 
this can be achieved by first detecting and segmenting the fish in every grayscale 
image of the incoming video stream and then translate this found fish contour  
to the range image obtaining a estimation of the volume.
To find the algorithm that is in line with our problem,
we need to understand the challenge in detecting fishes.
they include the motion of the fish which makes the object of interest deformable,
the location of the fish respect to the camera and occlusions caused by having 
multiple fishes in every available frame.

In this project, we concentrate on the first step that is detection of the fish 
that undergo deformation in grayscales images. we propose an approach inspired by 
two works from, the first, 
\citet{ramanan2012} which describe a method for articulated human detection
and human pose estimation in static images based on a representation of deformable 
part models. The main idea of their approach is to use a mixture of small, non-oriented 
parts, which describe a general, flexible mixture model that jointly captures spatial 
relations between parts locations and co-occurrences relations between part mixtures, 
augmenting standard pictorial structure models that encode just spatial relations. 
The second approach is propose in \citet{Hinterstoisser2012}, where they present 
a method for real-time 3D object instance detection that does not require a time 
consuming training stage, and can handle untextured objects. At its core, the approach 
presented is a novel image representation for template matching designed to be robust 
to small image transformations, This robustness is based on spread image gradient 
orientations and allows to test only a small subset of all possible pixel locations 
when parsing a image.

We evaluate the proposes method by computing difference between the labeled dataset
with the predicted result, in addition, we cluster the results from different 
camera locations and found that when the sagittal plane is parallel to the image plane,
the tracking algorithm provide the best result.
% Finally, we show that \todo { show improvement}.

Therefore, In this thesis, we accomplished  the goals of creating a annotated datasets that
comprise of learning keypoints and fish contours from a set of 2D grayscale images.
We also implement a combine solution from a part based detection model and a template
matching detection approach, which is capable of predict keypoints and fish contours in an 
unlabeled 2d grayscale image and verifying the validity of the prediction.
