\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}	


%\chapter*{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \bf Acknowledgments}
\end{center}

\vspace{1cm}

I have a great deal of people to thank for the presented work, but the most important
one is my wife, who left everything behind in our home country to be with me in this
adventure, Without her company, support and affection, I could not fulfill
my dream of studying in Germany.
Also, I would like to thank my family for their outstanding support for the entire
duration of my course.

I thank Dr. Slobodan Ilic and Prof. Dr. Nassir Navab as they
play important roles in the completion of this thesis. In addition, I acknowledge the
help from the Computer Vision group at the Chair for Computer Aided Medical Procedures
and Augmented Reality. Furthermore, I would like to specifically mention the contribution
of David Tan, for sharing his knowledge during our project in the field of deformable
object detection in underwater applications.

Also, I would like to thank to three compatriot, who make my stay in the TU M{\"u}nchen possible, 
Dr. Victor Casta\~{n}eda for help me during my application to the program and
the beginning of this process, Jose Gardiazabal for offering always a hand 
when I need it and Eduardo Morral to offered me accommodation during the tough task of 
find a place to live in M{\"u}nchen.

Finally, it is a pleasure to  thank who made this possible. I want to thank the Chilean National
Commission for Science and Technology $(CONICYT)$, whose funding and confidence have
done possible to carry out my project in Germany.




